Ants-Review: A Protocol For Open Anonymous Peer-Reviews

### 2020-07-28 paper-v1.tex
Proof of Existence [merkle tree/proof of work removed] w/ @naszam

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS}, a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data immutability and unique file identification via cryptographic hashes.
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system still engages into maintaining the privacy of both authors and reviewers in a double-blind approach.

@@

In the following sections we describe the architecture of the system and its building blocks.
\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities as shown in the flow-chart (See Figure \ref{fig:contracts}):
\emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
\emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).

@@

Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts} \textbf{b}). It's implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts. In this way, only the Issuer can create a new AntReview.
\newline One of the key aspects of the protocol is the concept of Proof of Existence. In Ethereum \cite{Ethereum} the concept of immutability is achieved via the blockchain and the proof of work consensus algorithm by a chain of timestamped block merkle tree root hashes that are secured by miners competing computations.

>>>>

\paragraph{Accountability via pseudo-anonymity.} In order to counteract malicious behaviour (see 2.1) affecting the integrity of the reviews but also to correctly attribute the intellectual contributions making sure there are no conflict of interest, it's important to be able to track back the identities of the contributors to a peer-review report. This is possible if the platform acts like a version control system where commits are permanent and their hashes timestamped. InterPlanetary File System (IPFS) \cite{IPFS} is a peer-to-peer hypermedia protocol for storing data in a distributed file system over the internet which guarantees data \emph{immutability} and unique file identification via cryptographic hashes. IPFS's hashes are then stored inside the smart contracts' state that is timestamped in the Ethereum Blockchain where it remains unaltered and indelible. This notarization process is called Proof of Existence (PoE).
\newline To prevent retaliation for negative peer-reviews and to promote the participation of early researchers who might feel intimidated to judge the scientific work of senior authors, the Ants-Review system maintains the privacy of both authors and reviewers in a double-blind approach.

@@

In the following sections we describe the architecture of the system and its building blocks.
\newline The Ants-Review Protocol is divided into different modules responsible for the following functionalities, as shown in the flow-chart (See Figure \ref{fig:contracts}):
\emph{AntsReview}, which manages access management and the core system (See Figure \ref{fig:contracts} \textbf{a,b,f,h}).
\emph{Tokenomics}, which manages the incentive mechanism of the system (See Figure \ref{fig:contracts} \textbf{c,d,e,h}).
\emph{Privacy}, which maintains the anonymity of the system via AZTEC Protocol (See Figure \ref{fig:contracts} \textbf{d}).

@@

Access management of the Ants-Review protocol is defined and controlled by AntsReviewRoles (See Figure \ref{fig:contracts} \textbf{b}). It's implemented by leveraging on \emph{AccessControl.sol} by OpenZeppelin Solidity Library\footnote[8]{\emph{OpenZeppelin Library}.\textsc{URL:}https://openzeppelin.com.}, through the creation of the Issuer and Peer-Reviewer Roles.
\newline It also integrates a circuit breaker design pattern via \emph{Pausable.sol} by OpenZeppelin to allow the Pauser Role, that by default is the Owner of the smart contracts, able to pause (or unpause) the functions in case of a security emergency, such as an attack to the smart contracts. In this way, only the Issuer can create a new AntReview.
